cvx-flats

### 2020-05-19 neurips-20/cvx-flats-statements.tex
Late night edits, starting a proof of calibrated iff (D)

\begin{lemma}\label{lem:consistent-loss-implies-prop}
	If $(L, \psi)$ are consistent with respect to $\ell$, then they are consistent with respect to $\gamma := \prop{\ell}$.
\end{lemma}
\begin{proof}
	\jessie{TODO}
\end{proof}

@@

	$\impliedby$ \jessie{zhang 04 corollary}
\end{proof}

>>>>

\begin{lemma}\label{lem:consistent-loss-implies-prop}
	If $(L, \psi)$ are consistent with respect to $\ell$, then they are consistent with respect to $\gamma := \prop{\ell}$.
\end{lemma}
\begin{proof}
	Define $\mu^\gamma(r, p) := R_\ell(r;p)$.
	Now suppose 
	\jessie{TODO}
\end{proof}

@@

	$\impliedby$ Consider $\zeta(c) := \inf_{u: R_L(u;p) \geq c} R_\ell(\psi(u); p)$.for nonnegative values of $c$, and $\zeta(c) = 0$ for $c < 0$.
	We will show $R_L(u_m; p) \to 0 \implies R_\ell(\psi(u_m); p) \to 0$ gives calibration via the function $\zeta$ constructed above.

	\jessie{Outline: 1. $\zeta$ satisfies requirements (A).  2. Verify bound is true as approach $0$ by assumption on regrets. 3. Verify bound is true elsewhere by construction of $\zeta$.}

	First, we can verify that $\zeta$ as constructed maps is continuous at $0$ and $\zeta(0) = 0$.
	\jessie{continuous: TODO}
	As $\risk{L}$ and $\risk{\ell}$ are well-defined for all $p \in \simplex$, taking $u = \Gamma(p)$ yields $\zeta(0) = \inf_u (R_\ell(\psi(u); p))$, which is $0$ as long as there is some $u$ so that $\psi(u) = \gamma(p)$ for each $p \in \simplex$.

	Second, we want to verify that the bound in Equation~\ref{eq:calibrated-general} holds as regrets approach $0$.
	Fix $p \in \simplex$.
	If $\{u_m\}$ is a sequence so that $R_L(u_m; p) \to 0$, then $\zeta(R_L(u_m; p)) \to 0$.
	As $R_\ell(\psi(u_m); p) \to 0$, then $\zeta$ of surrogate regret upper bounds discrete regret as surrogate regret gets arbitrarily close to $0$.

	Last, we observe that the bound in Equation~\eqref{eq:calibrated-general} is satisfied for $\{u_m\} \not \to 0$ by construction of $\zeta$.	
	\jessie{TODO}
\end{proof}
